\documentclass[12pt]{article}
% \documentstyle{iascars2017}

% \usepackage{iascars2017}

\pagestyle{myheadings} 
\pagenumbering{arabic}
\topmargin 0pt \headheight 23pt \headsep 24.66pt
% \topmargin 11pt \headheight 12pt \headsep 13.66pt
\parindent = 3mm 


\begin{document}


\begin{flushleft}


{\LARGE\bf Model-checking  for regressions: a local smoothing-based global smoothing test}


\vspace{1.0cm}

Lingzhu Li$^1$ and Lixing Zhu$^2$

\begin{description}

\item $^1 \;$ Department of Mathematics, Hong Kong Baptist University, Hong Kong

\item $^2 \;$ Department of Mathematics, Hong Kong Baptist University, Hong Kong

\end{description}

\end{flushleft}

%  ***** ADD ENOUGH VERTICAL SPACE HERE TO ENSURE THAT THE *****
%  ***** ABSTRACT (OR MAIN TEXT) STARTS 5 CM BELOW THE TOP *****

\vspace{0.75cm}

\noindent {\bf Abstract}. As the two kinds of methods for  model specification problem, local smoothing tests and global smoothing tests exhibit different characteristics.
Compared with global smoothing tests, local smoothing tests can only detect local alternatives distinct from the null hypothesis at a much   slower rate when the dimension of predictor vector is high, but can be more sensitive to high-frequency alternatives.
We suggest a projection-based test that builds a bridge between the local and global smoothing methodologies to benefit from their own advantages.
The test construction is based on a kernel estimation-based local smoothing method and the resulting test becomes a distance-based global smoothing test.
A closed-form expression of the test statistic is derived and the asymptotic properties are investigated.
Simulations and a real data analysis are conducted to evaluate the performance of the test in finite sample cases.

\vskip 2mm

\noindent {\bf Keywords}. Global smoothing test, projection-based methods, local smoothing test


\subsection*{References}

\begin{description}
\item
Zheng, J. X. (1996).
\textit{Journal of Econometrics: A consistent test of functional form via nonparametric estimation techniques},
\textbf{75(2)}, 263--289.

\item
Bierens, H. J. (1982).
\textit{Journal of Econometrics: Consistent model specification tests},
\textbf{20}, 105-134.

\item
Lavergne, P. and Patilea, V. (2012).
\textit{Journal of business \& economic statistics: One for all and all for one: regression checks with many regressors.}
\textbf{30(1)}, 41--52. 
Taylor \& Francis Group.

% \item
% Escanciano, J. C. (2006).
% \textit{Econometric Theory: A consistent diagnostic test for regression models using projections.}
% \textbf{22(6)}, 1030--1051.


\end{description}

\end{document}





