\documentclass[12pt]{article}
% \documentstyle{iascars2017}

% \usepackage{iascars2017}
\usepackage{hyperref}

\pagestyle{myheadings} 
\pagenumbering{arabic}
\topmargin 0pt \headheight 23pt \headsep 24.66pt
%\topmargin 11pt \headheight 12pt \headsep 13.66pt
\parindent = 3mm 


\begin{document}


\begin{flushleft}


{\LARGE\bf Visualization and Statistical Modeling of Financial Big Data}


\vspace{1.0cm}

Masayuki Jimichi$^1$, Daisuke Miyamoto$^2$, Chika Saka$^1$, and Syuichi Nagata$^1$


\begin{description}

\item $^1 \;$ 
School of Business Administration, Kwansei Gakuin University, 
Nishinomiya, Uegahara, 
662-8501, 
Japan

\item $^2 \;$ Graduate Schook of Information Science, Nara Institute of Science and Technology, 
8916-5 Takayama-cho, Ikoma, Nara 630-0192, Japan

\end{description}

\end{flushleft}

\vspace{0.75cm}

\noindent {\bf Abstract}. 
In this work, we manipulate financial big data of world-wide companies by R packages SparkR and sparklyr, 
and treate data visualization (e.g. Ihaka, 2017;  Unwin, 2015) and statistical model (e.g. Chambers and Hastie, 1991) based on exploratory data analysis (Tukey, 1977) with R. The dataset is extracted from the database systems by Bureau van Dijk KK which contains information on over 80,000 listed companies. 
We find that a log-skew-t linear model (e.g. Azallini and Capitanio, 2014) is very useful for explaining sales by employees and assets.

\vskip 2mm

\noindent {\bf Keywords}.
Financial Big Data, Data Visualization, Statistical Modeling, Log-skew-t Linear Model, SparkR, sparklyr

\subsection*{References}

\begin{description}\itemsep-4pt\parsep0pt

\item
Azzalini, A. with the collaboration of Capitanio, A. (2014). 
\textit{The Skew-Normal and Related Families}. 
Cambridge University Press. 
Institute of Mathematical Statistics Monographs.

\item
Chambers, J. M. and Hastie,  T. J. ed. (1991).
\textit{Statistical Models in S}. 
Chapman and Hall/CRC. 

\item
Ihaka, R. (2017). Lecture Notes. 
\url{https://www.stat.auckland.ac.nz/~ihaka/?Teaching}

\item
Tukey, J. W. (1977).
\textit{Exploratory Data Analysis}. 
Addison-Wesley Publishing Co.

\item
Unwin, A. (2015). 
\textit{Graphical Data Analysis with R}, 
Chapman and Hall/CRC. 
\end{description}

\end{document}





