\documentclass[12pt]{article}
% \documentstyle{iascars2017}

% \usepackage{iascars2017}

\pagestyle{myheadings} 
\pagenumbering{arabic}
\topmargin 0pt \headheight 23pt \headsep 24.66pt
%\topmargin 11pt \headheight 12pt \headsep 13.66pt
\parindent = 3mm 


\begin{document}


\begin{flushleft}


{\LARGE\bf Transfer Regression and Predictive Distributions}


\vspace{1.0cm}
Shigetoshi Hosaka$^1$
and
Jinfang Wang$^2$


\begin{description}
\item $^1 \;$ Hosaka Clinic of Internal Medicine, Tokyo, Japan
\item $^2 \;$ Department of Mathematics and Informatics, Graduate School of Science, Chiba University, Japan
\end{description}

\end{flushleft}

%  ***** ADD ENOUGH VERTICAL SPACE HERE TO ENSURE THAT THE *****
%  ***** ABSTRACT (OR MAIN TEXT) STARTS 5 CM BELOW THE TOP *****

\vspace{0.75cm}

\noindent {\bf Abstract}. 
We introduce the \textit{transfer regression}, a method for constructing prior distributions for parameters defining generalized linear models (GLM).
The transfer regressions are based frequency tables, usually obtained by categorizing the continuous variables.
So obtained prior information are transferred to the parameters defining the second stage GLM based on detailed data.
at the second stage based on more detailed data. 
We illustrate these ideas by showing how to compute posterior predictive probabilities of contracting diabetes based on HbA1c data obtained from comprehensive medical examinations. 

\noindent {\bf Keywords}.
Bayesian generalized linear models, Markov chain Monte Carlo methods, posterior predictive distributions


%\section{ First-level heading}
%The C98 head 1 style leaves a half-line spacing below a
%first-level heading. There should be one blank line above
%a first-level heading.
%        
%\subsection { Second-level heading}
%There should also be one blank line above a second- or
%third-level heading (but no extra space below them).
%
%Do not intent the first paragraph following a heading.
%Second and subsequent paragraphs are indented by one Tab
%character (= 3 mm). If footnotes are used, they should be
%placed at the foot of the page\footnote{ Footnotes are separated
%from the text by a blank line and a printed line of length 3.5 cm.
%They should be printed in 9-point Times Roman in single line spacing.}.
%        
%\subsubsection { Third-level heading}
%Please specify references using the conventions
%illustrated below. Each should begin on a new line, and
%second and subsequent lines should be on the same page
%indented by 3 mm.

\subsection*{References}

\begin{description}

\item

Andrew D. Martin, Kevin M. Quinn and Jong Hee Park (2011).
MCMCpack: Markov Chain Monte Carlo in R,
\textit {Journal of Statistical Software}, \textbf {42}, 1--21.
%\url{http://www.jstatsoft.org/v42/i09/}.

\item
Kass, R. E. and Wasserman, L. (1996).
The Selection of Prior Distributions by Formal Rules,
\textit {Journal of the American Statistical Association}, \textbf {91}, 1343--1370.

\item 
Wang, J. and Hosaka, S. (2017). Cell regression and reference prior,
Symposium on ``\textit {Statistical Modelling and Computational Algorithms}", at Nagoya University, Febuary 18--19, 2017.

\end{description}

\end{document}





