\documentclass[12pt]{article}
% \documentstyle{iascars2017}

% \usepackage{iascars2017}

\pagestyle{myheadings} 
\pagenumbering{arabic}
\topmargin 0pt \headheight 23pt \headsep 24.66pt
%\topmargin 11pt \headheight 12pt \headsep 13.66pt
\parindent = 3mm 


\begin{document}


\begin{flushleft}


{\LARGE\bf Simultaneous test for mean vectors and covariance matrices 
in high-dimensional settings}


\vspace{1.0cm}

Takahiro Nishiyama$^1$ and Masashi Hyodo$^2$

\begin{description}

\item $^1 \;$ Department of Business Administration, Senshu University, 
2-1-1, Higashimita, Tama-ku, Kawasaki-shi, Kanagawa 214-8580, Japan

\item $^2 \;$ Department of Mathematical Sciences, Graduate School of Engineering, 
Osaka Prefecture University, 
1-1 Gakuen-cho, Naka-ku, Sakai, Osaka 599-8531, Japan

\end{description}

\end{flushleft}

%  ***** ADD ENOUGH VERTICAL SPACE HERE TO ENSURE THAT THE *****
%  ***** ABSTRACT (OR MAIN TEXT) STARTS 5 CM BELOW THE TOP *****

\vspace{0.75cm}
\renewcommand{\vec}[1]{\mbox{\boldmath ${#1}$}}

Let $\vec{X}_{g1}$, $\vec{X}_{g2}$, $\ldots$, $\vec{X}_{gn_g}$ be 
i.i.d. random samples of size $n_{g}$ from a $p$-dimensional 
population $\Pi_g$ ($g \in \{1, 2\}$) with ${\rm E}(\vec{X}_{gi})=\vec{\mu}_g$ 
and ${\rm var}(\vec{X}_{gi})=\Sigma_g$ ($i \in \{1, \ldots ,n_g\}$). 
In this talk, our primary interest is to test following hypothesis 
when $p > \min\{n_1-1, n_2-1 \}$: 
\begin{eqnarray*}
H_0 : \vec{\mu}_1 = \vec{\mu}_1,~ \Sigma_1 = \Sigma_2 \quad 
\mbox{vs.} \quad H_1 : \mbox{not}~ H_0.
\end{eqnarray*}

For this problem, we discuss an $L^2$-norm-based test for simultaneous 
testing of mean vectors and covariance matrices among two non-normal populations. 
To construct a test procedure, we propose a test statistic based on both unbiased 
estimator of differences mean vectors proposed by Chen and Qin (2010) 
and covariance matrices proposed by Li and Chen (2012). 
Also, we derive an asymptotic distribution of this test statistic 
and investigate the asymptotic sizes and powers of the proposed test. 
Finally, we study the finite sample and dimension performance 
of this test via Monte Carlo simulations.

\vskip 2mm

\noindent {\bf Keywords}.
Asymptotic distribution, High-dimensional data analysis, Testing hypothesis 


\subsection*{References}

\begin{description}

\item
Chen, S.X. and Qin, Y.L. (2010). 
A two-sample test for high dimensional data with applications to
gene-set testing. 
\textit{Ann. Statist.},
\textbf{38}, 808--835. 

\item
Li, J and Chen, S.X. (2012). 
Two sample tests for high-dimensional covariance matrices. 
\textit{Ann. Statist.},
\textbf{40}, 908--940. 

\end{description}

\end{document}





